---
title: "FDS Final Project: Report #4"
output: html_document
---

```{r}
library(dplyr)
library(readxl)
library(ggplot2)
library(stringr)
library(tidyr)
library(rlang)

```

#Part1



```{r}
medals <- read_excel("olympics.xlsx", sheet = "medals")
athletes <- read_excel("olympics.xlsx", sheet = "athletes")
country <- read_excel("olympics.xlsx", sheet = "country")
games <- read_excel("olympics.xlsx", sheet = "games")

# Check if there are any athletes who competed for different countries over time
athletes_with_multiple_countries <- medals %>%
  group_by(athlete_id) %>%
  summarise(Num_Country = n_distinct(Team), .groups = "drop") %>%
  filter(Num_Country > 1)

# Print the result
print(athletes_with_multiple_countries)
```

Name 
116, Hosni Mohamed Abbas
193, Dorri Abdel Kader Said
195, Mohamed Ali Abdel Kerim
206, Amin Abdel Rahman
211, Sameh Abdel Rahman
359, Andrey Khakimovich Abduvaliyev
360  Dzhamolidin Mirgarifanovich Abduzhaparov
363  Kazumi Abe
484  Abdel Fattah Abou-Shanab
550  Dmitry Vladimirovich Abramovich





#Part2

```{r}
top_athletes_by_games <- country %>%
  group_by(athlete_id) %>%
  summarise(Num_Games = n_distinct(Games), .groups = "drop") %>%
  arrange(desc(Num_Games)) %>%
  slice_head(n = 10)

print(top_athletes_by_games)
```

Name

79855	Ian Millar			
65378	Afanasijs Kuzmins			
99155	Hubert Raudaschl			
14388	Stefania Stanzani			
26880	Rajmond Debevec			
28051	Piero D'Inzeo			
28052	Raimondo D'Inzeo			
32458	Paul Bert Elvstrm			
51618	Josefa Idem-Guerrini			
61572	Durward Randolph Knowles

Part 3: What athlete(s) kept a Gold medal for the longest time?

```{r}

gold_medal_winners <- medals %>%
  filter(Medal == "Gold")

gold_medal_winners$Year <- as.integer(str_extract(gold_medal_winners$Games, "\\d+"))

gold_medal_winners <- gold_medal_winners %>%
  arrange(athlete_id, Event, Year)

gold_medal_winners <- gold_medal_winners %>%
  group_by(athlete_id, Event) %>%
  mutate(consecutive_wins = c(0, diff(Year) == 4))

gold_medal_winners <- gold_medal_winners %>%
  group_by(athlete_id, Event) %>%
  mutate(streak = cumsum(consecutive_wins))

max_streaks <- gold_medal_winners %>%
  group_by(athlete_id, Event) %>%
  summarise(max_streak = max(streak), .groups = "drop")

longest_streaks <- max_streaks %>%
  arrange(desc(max_streak)) %>%
  slice_head(n = 10)

print(longest_streaks)

```
Name 

39726	 Aladr Gerevich (-Gerei)
11671	 Ossian Esaias Skild
19044	 David Toivo Teivonen
32458	 Paul Bert Elvstrm
47137	 Jayna Hefford
57699	 Rudolf Krpti
63409	Pl dm Kovcs
68985 Lisa Deshawn Leslie (-Lockwood)	
69210	Frederick Carlton "Carl" Lewis
70965 Ryan Steven Lochte

Part 4: What country(ies) kept a Gold medal for the longest time?

```{r}

gold_medal_winners <- medals %>%
  filter(Medal == "Gold")

gold_medal_winners$Year <- as.integer(str_extract(gold_medal_winners$Games, "\\d+"))

gold_medal_winners <- gold_medal_winners %>%
  arrange(Team, Event, Year)

gold_medal_winners <- gold_medal_winners %>%
  group_by(Team, Event) %>%
  mutate(consecutive_wins = c(0, diff(Year) == 4))

gold_medal_winners <- gold_medal_winners %>%
  group_by(Team, Event) %>%
  mutate(streak = cumsum(consecutive_wins))

max_streaks <- gold_medal_winners %>%
  group_by(Team, Event) %>%
  summarise(max_streak = max(streak), .groups = "drop")

longest_streaks <- max_streaks %>%
  arrange(desc(max_streak)) %>%
  slice_head(n = 10)

print(longest_streaks)

```

Part 5: Who are the ten athletes that competed in the most events?


# Get the ten athletes who competed in the most events

```{r}
top_athletes_by_events <- medals %>%
  group_by(athlete_id) %>%
  summarise(Num_Events = n_distinct(Event), .groups = "drop") %>%
  arrange(desc(Num_Events)) %>%
  slice_head(n = 10)

print(top_athletes_by_events)

```

Part 6: Create a new table showing the number of medals per country and per year

```{r}
medals$Year <- as.integer(str_extract(medals$Games, "\\d+"))

medals_by_country_year <- medals %>%
  group_by(Team, Year) %>%
  summarise(Num_Medals = n(), .groups = "drop")

top_countries <- medals_by_country_year %>%
  group_by(Team) %>%
  summarise(Total_Medals = sum(Num_Medals), .groups = "drop") %>%
  arrange(desc(Total_Medals)) %>%
  slice_head(n = 15) %>%
  pull(Team)


medals_by_country_year <- medals_by_country_year %>%
  filter(Team %in% top_countries)


medals_by_country_year_wide <- medals_by_country_year %>%
  pivot_wider(names_from = Year, values_from = Num_Medals, values_fill = 0)

print()
print.default()

```


Part 7: Is there a relationship between country and the probability of winning a medal?

```{r}


medals_participated <- medals %>%
  filter(Team %in% top_countries) %>%
  group_by(Team) %>%
  summarise(Total_Medals_Won = n(),
            Total_Events_Participated = n_distinct(Event),
            .groups = "drop")

medals_participated$Percentage_Medals_Won <- medals_participated$Total_Medals_Won / medals_participated$Total_Events_Participated * 100

ggplot(medals_participated, aes(x = reorder(Team, Percentage_Medals_Won), y = Percentage_Medals_Won)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Country", y = "Percentage of Medals Won", title = "Percentage of Medals Won out of All Medals Competed for by Country")

```
#Based on your observation, it seems that countries such as the USA, UK, France, Italy, and Japan have significantly larger bars compared to countries like Switzerland or Finland. This suggests that athletes from the former group of countries win a higher proportion of medals compared to the total number of events they compete in.

```{r}
medals$Medal_Won <- ifelse(!is.na(medals$Medal), "Yes", "No")

medals_top_countries <- medals %>%
  filter(Team %in% top_countries)

contingency_table <- table(medals_top_countries$Team, medals_top_countries$Medal_Won)

chi_square_test <- chisq.test(contingency_table)

print(chi_square_test)

```
#


Part 8: Create a scatterplot showing the average height versus the average weight of competitors per sport
```{r}


athletes_medals <- athletes %>%
  left_join(medals, by = c("ID" = "athlete_id"))

average_stats_per_sport <- athletes_medals %>%
  group_by(Sport) %>%
  summarise(Average_Height = mean(Height / 100, na.rm = TRUE),  # Convert height to meters
            Average_Weight = mean(Weight, na.rm = TRUE),
            Average_BMI = mean(Weight / (Height / 100)^2, na.rm = TRUE),
            .groups = "drop")

labels <- average_stats_per_sport %>%
  summarise(Largest_Height_Sport = Sport[which.max(Average_Height)],
            Largest_Weight_Sport = Sport[which.max(Average_Weight)],
            Smallest_Height_Sport = Sport[which.min(Average_Height)],
            Smallest_Weight_Sport = Sport[which.min(Average_Weight)],
            Largest_BMI_Sport = Sport[which.max(Average_BMI)],
            Smallest_BMI_Sport = Sport[which.min(Average_BMI)])

ggplot(average_stats_per_sport, aes(x = Average_Height, y = Average_Weight)) +
  geom_point() +
  geom_text(data = subset(average_stats_per_sport, Sport %in% unlist(labels)), aes(label = Sport), hjust = -0.1, vjust = -0.1) +
  labs(x = "Average Height (m)", y = "Average Weight (kg)", title = "Average Height vs Average Weight by Sport")

```


Part 9: Create a line plot showing the number of medals given by year

```{r}

medals_games <- medals %>%
  left_join(games, by = "Games")

medals_by_year <- medals_games %>%
  filter(!is.na(Medal)) %>%
  group_by(Year.x, Medal, Season) %>%
  summarise(Num_Medals = n(),
            .groups = "drop")

ggplot(medals_by_year, aes(x = Year.x, y = Num_Medals, color = Medal)) +
  geom_line() +
  facet_grid(Season ~ .) +
  labs(x = "Year", y = "Number of Medals",
       color = "Medal Type",
       title = "Number of Medals by Year and Medal Type",
       subtitle = "Faceted by Season (Summer or Winter Games)")

```



