---
title: "FDS Final Project: Report #3"
output: html_document    
---
#PART 1   

- What are the highest grossing dramas from 2010?
- Have Will Ferrell and Liam Neeson even been in a movie together?
- Can you find kids movies with Tom Cruise in it?

```{r}
library(httr)
library(dplyr)
library(purrr)
library(ggplot2)
library(jsonlite)
```

```{r}
make_api_request <- function(url) {
  response <- GET(url)
  stop_for_status(response)
  content(response, as = "parsed")
}

convert_to_tibble <- function(result) {
  as_tibble(result)
}


print_movie_titles <- function(result) {
  if ("results" %in% names(result)) {
    movies <- result$results
    if (length(movies) > 0) {
      cat("Movie Titles:\n")
      for (movie in movies) {
        cat(movie$title, "\n")
      }
    } else {
      cat("No movies found.\n")
    }
  } else {
    cat("Invalid response format.\n")
  }
  cat("\n")
}

base_url <- "https://api.themoviedb.org/3/search/movie"


api_key <- ""

queries <- list(
  "highest_grossing_dramas_2010" = list(query = "drama", year = "2010"),
  "will_ferrell_liam_neeson_movie" = list(query = "Will Ferrell Liam Neeson"),
  "kids_movies_with_tom_cruise" = list(query = "kids", actor = "Tom Cruise")
)


for (query_name in names(queries)) {
  query_params <- queries[[query_name]]
  
 
  full_url <- modify_url(base_url, query = c(query_params, api_key = api_key))
  
  cat("Query:", query_name, "\n")
  cat("URL:", full_url, "\n")
  
  result <- make_api_request(full_url)
  print_movie_titles(result)
}
```



#Part 2 From `RStudio`, what query would you make to find the id of the animation movie company "Pixar"? 
Show both the query and how you extract the id from the result in your report.


```{r}
query <- "Pixar"

full_url <- modify_url(base_url, query = list(query = query, api_key = api_key))
result <- make_api_request(full_url)

if ("results" %in% names(result) && length(result$results) > 0) {
  pixar_id <- result$results[[1]]$id
  cat("Company 'Pixar' has the following id:", pixar_id, "\n")
} else {
  cat("Company 'Pixar' not found.\n")
}
```
#PART 3 
Finding all Pixar movies and sorting by revenue

```{r}
query_params <- list(
  with_companies = "Pixar Animation Studios",
  sort_by = "revenue.desc",
  api_key = "197aac93c3e105765e64e0d49c5faad2"
)

full_url <- modify_url(base_url, query = query_params)
result <- make_api_request(full_url)

total_pages <- result$total_pages

movies <- as_tibble(result$results)

print(movies)


movies <- as_tibble(result)


all_movies <- map_df(2:total_pages, function(page) {
  query_params$page <- page
  full_url <- modify_url(base_url, query = query_params)
  response <- make_api_request(full_url)
  convert_to_tibble(response)
})


print(all_movies)
```

#PART 4 


```{r}
make_api_request <- function(url) {
  response <- GET(url)
  stop_for_status(response)
  content(response, as = "parsed")
}

filter_popular_films <- function(films) {
  films %>%
    filter(vote_count >= 50)
}

base_url <- "https://api.themoviedb.org/3"

api_key <- ""

query <- "Walt Disney Pictures"
query_params <- list(query = query, api_key = api_key)
company_search_url <- modify_url(paste0(base_url, "/search/company"), query = query_params)

company_search_result <- make_api_request(company_search_url)

disney_company_id <- company_search_result$results %>%
  filter(name == "Walt Disney Pictures" & origin_country == "US") %>%
  select(id) %>%
  pull()

disney_query_params <- list(
  with_companies = disney_company_id,
  primary_release_date_gte = "2006-01-01",
  api_key = api_key
)
disney_movies_url <- modify_url(paste0(base_url, "/discover/movie"), query = disney_query_params)

pixar_query_params <- list(
  with_companies = "3",  # Pixar company ID is 3
  primary_release_date_gte = "2006-01-01",
  api_key = api_key
)
pixar_movies_url <- modify_url(paste0(base_url, "/discover/movie"), query = pixar_query_params)

disney_movies_result <- make_api_request(disney_movies_url)
pixar_movies_result <- make_api_request(pixar_movies_url)

disney_movies <- filter_popular_films(disney_movies_result$results)
pixar_movies <- filter_popular_films(pixar_movies_result$results)

comparison_data <- rbind(
  data.frame(Company = "Disney", Vote_Average = disney_movies$vote_average),
  data.frame(Company = "Pixar", Vote_Average = pixar_movies$vote_average)
)


ggplot(comparison_data, aes(x = Company, y = Vote_Average)) +
  geom_boxplot() +
  labs(x = "Company", y = "Vote Average", title = "Comparison of Vote Averages: Disney vs. Pixar")


t_test_result <- t.test(Vote_Average ~ Company, data = comparison_data)
cat("\nT-Test Results:\n")
print(t_test_result)
```

